Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Use property or example instead of evidence, it fit's better here

\noindent The {\tt it} function combines a text description and
an evidence and makes a spec.
Examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

@@

A spec can be run with the \texttt{hspec} function.  When a spec is run, all
evidence are evaluated, and failing evidence are reported to developers.

>>>>

\noindent The {\tt it} function combines a text description for a
behavior and a property or an example that gives some confidence in
that behavior into a spec.
Examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

@@

A spec can be run with the \texttt{hspec} function.  When a spec is
run, all properties and examples are evaluated, and failing properties
and examples are reported to the developer.
